---
title: "ProjectTracking"
author: "Alison Whipple"
date: "November 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up Git Repo and R package environment

Discussion on how to do this: <https://community.rstudio.com/t/procedure-to-create-a-project-for-a-package-destined-for-github/2054>  
Used these steps for The “GitHub first” approach: 

* Create repo on GitHub (YES to Initialize this repository with a README)  
* Capture URL from the big green “Clone or download” button; new RStudio Project from that
* devtools::setup()
* Quit and Relaunch RStudio in this Project.

## Basic workflow

### Add functions to .R files

1. Write the function and load it with devtools::load_all() (Ctrl-Shift-L) and then see if it works
2. Document functions with roxygen syntax 

* Lines starting with #'
* Title is first line
* Description is two lines down
* Details follow (optional)
* @param sets the parameters (e.g., "@param x A number.")
* @import or @importFrom for all functions or selected functions in a package, respectively
* @export to say whether its exported from the package to be used by others
* @return to describe what is returned (e.g., "The sum of \\code{x} and \\code{y}")
* @examples to provide some examples

3. Update documentation: devtools::document() (or Ctrl-Shift-D) and preview with ?

### Update DESCRIPTION

If functions depend on packages, add them in DESCRIPTION as "depends", "imports", or "suggests" - only use "depends" for packages this is totally dependent upon (i.e., raster package)

## Loading package and checking

Installing the package: Load the devtools library, then in the Build tab, click Install and Restart (Ctrl-Shift-B)

Checking the package: run devtools::check() (Ctrl-Shift-E)

Note that this does not build vignettes

## Testing

1. Modify code or tests
2. Test package with devtools::test() (Ctrl-Shift-T)

See Wickham Testing chapter

## Package documentation

### Update the package-hydrospatial.R file

As decisions are made about the organization of the package, update this file

### Update the intro-vignette

See Wickham text for this

## Other

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
