---
title: "ProjectTracking"
author: "Alison Whipple"
date: "November 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up Git Repo and R package environment

Discussion on how to do this: <https://community.rstudio.com/t/procedure-to-create-a-project-for-a-package-destined-for-github/2054>  
Used these steps for The “GitHub first” approach: 

* Create repo on GitHub (YES to Initialize this repository with a README)  
* Capture URL from the big green “Clone or download” button; new RStudio Project from that
* devtools::setup()
* Quit and Relaunch RStudio in this Project.




When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
